Interval Probability and Measurement for Fuzzy Quantum Theories

### 2016-09-16 prob.tex
prob.tex \subsection{Classical Interval-valued probability measures} Updating...

\yutsung{Because the physical meaning of convex is still not clear,
it would be better if we can find or prove a theorem which removes
``convex'' in the theorem. However, I still have not found an interval-valued
probability measure with an empty core or proved that each interval-valued
probability measure has an nonempty core. What we know:
\begin{enumerate}
\item The cloud in \cite{JamisonLodwick2004} cannot induce an interval-valued
probability measure. Therefore, any results related to clouds cannot
be used directly.
\item The definition of interval-valued probability measure in \cite{JamisonLodwick2004}
is different from any later definition of interval-valued probability
measure written by Lodwick, including \cite{Lodwick2008}.
\item About linear programming, the answer of Mathematica program for $\left|\Omega\right|=3$
is too complex to read by human. May need to simplify the result to
a human readable one?
\item Check whether the Shapley value still in the core or not in our setting...?
\end{enumerate}
}

>>>>

For the general interval-valued probability measures, the following
theorem gives an algorithmic way to decide whether it has a non-empty
core.

\begin{thm}{[}Bondareva-Shapley~\cite{Shapley1967,Bondareva1968,Grabisch2016}{]}\label{thm:Bondareva-Shapley}
Let $l$ be the left-end of an interval-valued probability measure~$\bar{\mu}$,
$\bar{\mu}$ has an non-empty core if and only if for any minimal
balanced set~$\left\{ E_{i}\right\} _{i=1}^{N}$, we have $\tensor*[_{\mathbb{R}}]{\sum}{_{i=1}^{N}}\gamma_{i}l\left(E_{i}\right)\le1$,
where:
\begin{enumerate}
\item $\left\{ E_{i}\right\} _{i=1}^{N}$ is called balanced set if they
are distinct, $\emptyset\ne E_{i}\subsetneq\Omega$, and there exist
positive coefficient~$\left\{ \gamma_{i}\right\} _{i=1}^{N}$ such
that $\tensor*[_{\mathbb{R}}]{\sum}{_{i=1\textrm{ and }\omega\in E_{i}}^{N}}\gamma_{i}=1$
for all $\omega\in\Omega$.
\item A minimal balanced set is one that includes on other balanced set.
\end{enumerate}
\qed\end{thm}

The Bondareva-Shapley theorem can be used to algorithmically decide
non-empty core because the minimal balanced set can be generated by
an algorithm~\cite{Peleg1965}.
